### 2015-11-30 fundamentals/intro.tex
replaced 'current tools are typically privately distributed having been developed in industrial contexts' with 'current tools are typically distributed under restrictive rather than open source licenses, having been developed in industrial contexts or using commercial software platforms.'

To date, current tools are typically privately distributed rather than open
source, having been developed in industrial contexts. Additionally, having
often been developed for customized applications, many possess inflexible
architectures. Finally, many model only fleet-level dynamics of facilities and
materials rather than discrete resolution of those individual agents and
objects. When the DOE-NE Fuel Cycles Technologies Systems Analysis Campaign
developed requirements necessary in a next generation fuel cycle simulator,
three main failure modes were associated with those software choices.
First, they discourage targeted
contribution and collaboration among experts. Next, they hobble efforts to
directly compare modeling methodologies. Finally, they over-specialize,
rendering most tools applicable to only a subset of desired simulation
fidelities, scales, and applications. Those three constraints were identified
as presenting significant challenges to modeling fidelity, generality, efficiency,
robustness, and scientific transparency in the field of fuel cycle analysis
\cite{huff_next_2010}.

>>>>

To date, current tools are typically distributed under restrictive rather than open
source licenses, having been developed in industrial contexts or using 
commercial software platforms. Additionally, having
often been developed for customized applications, many possess inflexible
architectures. Finally, many model only fleet-level dynamics of facilities and
materials rather than discrete resolution of those individual agents and
objects. When the DOE-NE Fuel Cycles Technologies Systems Analysis Campaign
developed requirements necessary in a next generation fuel cycle simulator,
three main failure modes were associated with those software choices.
First, they discourage targeted
contribution and collaboration among experts. Next, they hobble efforts to
directly compare modeling methodologies. Finally, they over-specialize,
rendering most tools applicable to only a subset of desired simulation
fidelities, scales, and applications. Those three constraints were identified
as presenting significant challenges to modeling fidelity, generality, efficiency,
robustness, and scientific transparency in the field of fuel cycle analysis
\cite{huff_next_2010}.
